More than one Author with different Affiliations

### 2016-01-13 manuscript.tex
more edits, comments

\begin{figure}
\centering
\includegraphics[width=\linewidth]{figures/mt4labeled.png}
\caption{Admixture analysis for {\it Zea mays} spp. {\it mays}, {\it Zea mays} spp. {\it parviglumas}, and {\it Zea mays} spp. {mexicana} (Mex.) with K=4 source populations. }
\label{fig:admixture}
\end{figure}

As a demonstration of analyses in ANGSD-wrapper, we explore patterns of diversity in a single genomic region of a subset of domesticated maize and wild teosinte. We used resequenced samples from the HapMap2 project  and calculated summary statistics using a 10 megabase region on chromosome 10.\jri{cite Chia 2012 instead. include region \& mean depth, supp. table w/ sample names \& depth. include download link.}

We first use \X\ to estimate the site frequency spectrum (SFS) of both maize and its wild progenitor \texit{Zea mays} ssp. \textit{parviglumis}, assuming an inbreeding coefficient of $F=1$ since these are all highly inbred samples. 
Consistent with previous results \citep{hufford2012comparative}, we show that the maize SFS is skewed towards more intermediate-frequency variants (Figure \ref{fig:figure3}A-B), likely a result of the bottleneck associated with maize domestication.\jri{cite Tim} 
We find further evidence of the effect of domestication using \X, revealing lower levels overall levels of diversity in maize (Figure \ref{fig:figure3}C).\jri{fill in \X's with which A-W script we used. probably need to modify this to mention Tripsacum and generation of the ancestral seq. and which A-W script we used for that.}
Using \X, we then scan our example region for windows with elevated differentiation between maize and teosinte. 
The mean $F_{ST}$ in this region is \X, close to the genome-wide reported value of \X \citep{hufford2012comparative} .  
The \X windows in the 1\% tail of highest $F_{ST}$ values include genes several genes identified as potential targets of selection during domestication in \citep{hufford2012comparative}

We next include two samples of the related wild teosinte \textit{Zea mays} ssp. {mexicana} to assess evidence for admixture.  
Figure \ref{fig:admixture}) identifies previously unreported structure within the domesticated maize samples used in \citep{hufford2012comparative}

>>>>

\begin{figure}
\centering
\includegraphics[width=\linewidth]{figures/mt4labeled.png}
\caption{Admixture analysis for {\it Zea mays} spp. {\it mays}, {\it Zea mays} spp. {\it parviglumas}, and {\it Zea mays} spp. {mexicana} (\texit{mex}) with K=4 source populations. For a list of samples see Table \X. }
\label{fig:admixture}
\end{figure}

\jri{change Mex to mex and make italics in figure axis} As a demonstration of analyses in ANGSD-wrapper, we explore patterns of diversity in a single genomic region of a subset of domesticated maize and wild teosinte. We used resequenced samples from the HapMap2 project  and calculated summary statistics using a 10 megabase region on chromosome 10.\jri{cite Chia 2012 instead. include region \& mean depth, supp. table w/ sample names in order from fig. \& depth. include download link.}

We first use \X\ to estimate the site frequency spectrum (SFS) of both maize and its wild progenitor \textit{Zea mays} ssp. \textit{parviglumis}, assuming an inbreeding coefficient of $F=1$ since these are all highly inbred samples. \jri{do we worry that fig. 3 not graphs directly from A-W?}

Consistent with previous results \citep{hufford2012comparative}, we show that the maize SFS is skewed towards more intermediate-frequency variants (Figure \ref{fig:figure3}A-B), likely a result of the bottleneck associated with maize domestication.\jri{cite Tim} 
We find further evidence of the effect of domestication using \X, revealing lower levels overall levels of diversity in maize (Figure \ref{fig:figure3}C).\jri{fill in \X's with which A-W script we used. probably need to modify this to mention Tripsacum and generation of the ancestral seq. and which A-W script we used for that.}
Using \X, we then scan our example region for windows with elevated differentiation between maize and teosinte. 
The mean $F_{ST}$ in this region is \X, close to the genome-wide reported value of \X \citep{hufford2012comparative}.\jri{change if not true}  
The \X windows in the 1\% tail of highest $F_{ST}$ values include genes several genes identified as potential targets of selection during domestication in \citep{hufford2012comparative} \jri{see supp tables in Huff. make supp. table of genes in top 1\%. sorry to add, but this is cool \& demonstrates more stuff A-W can do. don't need a graph}

Finally, we include two samples of the related wild teosinte \textit{Zea mays} ssp. {mexicana} to assess evidence for admixture.  
Figure \ref{fig:admixture} identifies structure within the domesticated maize separating three high-latitude temperate landraces from the other tropical accessions. 
We find no evidence of admixture between these lowland maize samples and  ssp. {mexicana}, consistent with an independent analysis using SNP genotyping \jri{cite Hufford 2013 plos gen}.
\textit{Zea mays} ssp. {mexicana} clusters into its own group, along with a single accession of ssp. {parviglumis} collected from region in which many teosinte populations appear to be the result of admixture between the two subspecies \jri{cite Fang 2012}.  A single  ssp. {parviglumis} accession from the Northern extent of the range does not appear to be well-classified with these data, likely due to our relatively limited geographic and genomic sampling.
